---
title: "Design of Experiments"
author: "Yen"
date: "2018/3/20"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```
#1
As part of a larger experiment, Dale (1992) looked at six samples of a wetland soil undergoing a simulated snowmelt. Three were randomly se- lected for treatment with a neutral pH snowmelt; the other three got a reduced pH snowmelt. The observed response was the number of Copepoda removed from each microcosm during the first 14 days of snowmelt.

Reduced pH      Neutral pH  
256 159 149     54 123 248  

h6(Using randomization methods, test the null hypothesis that the two treatments have equal average numbers of Copepoda versus a two-sided alternative.

```{r}
ph <- c(256, 159, 149, 54, 123, 248)
s <- (sum(ph[1:3])-sum(ph[4:6]))/3
r <- NULL
for(i in 1:10000){
  ph1 <- sample(ph ,6,F)
  exp <-(sum(ph1[1:3])-sum(ph1[4:6]) )/3
  r <- c(r,exp)
}
ggplot(as.data.frame(r),aes(x = r))+
  geom_histogram(bins = 20)+
  geom_vline(xintercept = c(-46.333333,46.333333), color = "blue")+
  labs(title = "模擬結果",
         x = "r", y = "count")+
  theme(text  = element_text(size = 10 ,family = "STHeitiTC-Light"))
p_value <- (sum(r<=(-s))+sum(r>=s))/10000
```
```{r}
p_value
```



#2
Derive  
$\sum_{i=1}^{g}\sum_{j=1}^{n_i}(y_{ij}-\bar y{..})^2 = \sum_{i=1}^{g}n_i(\bar y_{i.}-\bar y_{..})^2+\sum_{i=1}^{g}\sum_{j=1}^{n_i}(\bar y_{ij}-\bar y{i.})^2$  

<proof>  
$\sum_{i=1}^{g}\sum_{j=1}^{n_i}(y_{ij}-\bar y{..})^2 = \sum_{i=1}^{g}\sum_{j=1}^{n_i}(y_{i.}-\bar y_{ij}+\bar y_{ij}-\bar y{..})^2\\=\sum_{i=1}^{g}\sum_{j=1}^{n_i}(y_{ij}-\bar y{i.})^2 +2 \sum_{i=1}^{g}\sum_{j=1}^{n_i}(y_{ij}-\bar y{i.})(\bar y_{i.}-\bar y{..})+\sum_{i=1}^{g}\sum_{j=1}^{n_i}(\bar y_{i.}-\bar y{..})^2$  

其中  

$\sum_{i=1}^{g}\sum_{j=1}^{n_i}(y_{ij}-\bar y{i.})(\bar y_{i.}-\bar y{..})=\sum_{i=1}^{g}(\bar y_{i.}-\bar y _{..})\sum_{j=1}^{n_i}(y_{ij}-\bar y_{i.})\\\sum_{j=1}^{n_i}(y_{ij}-\bar y_{i.}) = \sum_{i=1}^{ni}y_{ij}-n_i\bar y_i=0\\\therefore\sum_{i=1}^{g}\sum_{j=1}^{n_i}(y_{ij}-\bar y{i.})(\bar y_{i.}-\bar y{..})$

=>  
$\sum_{i=1}^{g}\sum_{j=1}^{n_i}(y_{ij}-\bar y{..})^2=\sum_{i=1}^{g}\sum_{j=1}^{n_i}(y_{ij}-\bar y{i.})^2+\sum_{i=1}^{g}\sum_{j=1}^{n_i}(\bar y_{i.}-\bar y{..})^2=\\\sum_{i=1}^{g}\sum_{j=1}^{n_i}(y_{ij}-\bar y{i.})^2+\sum_{i=1}^{g}n_i(\bar y_{i.}-\bar y{..})^2$

又  
$\bar y_{i.}-\bar y_{..}=\alpha_i$  
$\therefore \sum_{i=1}^{g}\sum_{j=1}^{n_i}(y_{ij}-\bar y{..})^2=\sum_{i=1}^gn_i\alpha_i+\sum_{i=1}^{g}\sum_{j=1}^{n_i}(y_{ij}-\bar y{i.})^2$



#3
$E(MSE)=E(\frac{SSE}{N-g})=\frac{1}{N-g}[(\sum_{i=1}^g(Y_{ij}-\bar Y_{i.})^2]\\=\frac{1}{N-g}\sum_{i=1}^{g}\sum_{j=1}^{n_i}Y_{ij}^2-2\sum_{i=1}^{g}\sum_{j=1}^{n_i}Y\bar Y_{i.}Y_{ij}+\sum_{i=1}^{g}\sum_{j=1}^{n_i}\bar Y_{i.}\\=\frac{1}{N-g}(\sum_{i=1}^{g}\sum_{j=1}^{n_i}E(Y_{ij})-\sum_{i=1}^{g}n_i\bar Y_{i.})\\=\frac{1}{N-g}\sum_{i=1}^{g}\sum_{j=1}^{n_i}(\sigma^2+\mu_i^2)\sum_{i=1}^{g}n_i(\frac{\sigma^2}{n_i}+\mu_i^2)\\=\frac{1}{N-g}(N\sigma^2+\sum_{i=1}^gn_i\mu_i^2-g\sigma^2-\sum_{i=1}^gn_i\mu_i^2)\\=\frac{1}{N-g}(N-g)\sigma^2=\sigma^2$

